Global SOC scenarios

### 2020-12-11 ResultNotebooks/results_SOCcompare.Rmd
update of results images and tables

SOCStock     <- dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=3)
glo_SOCStock <- dimSums(SOCStock, dim=1) 
cell2iso     <- toolGetMapping("CountryToCellMapping.csv", type = "cell")
iso_SOCStock <- toolCountryFill(toolAggregate(SOCStock, rel=cell2iso, from="celliso", to="iso", dim=1), fill=0)
iso2reg      <- read.csv2("Data/histManagement/regionmappingH12.csv")
reg_SOCStock <- toolAggregate(iso_SOCStock, rel=iso2reg, from="CountryCode", to="RegionCode")
```

@@

SOCStock <- mbind(glo_SOCStock, reg_SOCStock)
glo_SOC  <- mbind(setNames(SOCStock[,"y2010",],"SOC Budget"), 
                  setNames(LPJmL4[,"y2010",], "LPJmL4Paper"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"))

>>>>

SoilCarbon[,,c("naturalstate.crop")] <- SoilCarbon[,,c("naturalstate.natveg")]
SOCStock     <- dimSums(dimSums(SoilCarbon[,,c("naturalstate","actualstate")], dim=3.3)* Landuse, dim=3.2)
glo_SOCStock <- dimSums(SOCStock, dim=1) 
cell2iso     <- toolGetMapping("CountryToCellMapping.csv", type = "cell")
iso_SOCStock <- toolCountryFill(toolAggregate(SOCStock, rel=cell2iso, from="celliso", to="iso", dim=1), fill=0)
iso2reg      <- read.csv2("Data/histManagement/regionmappingH12.csv")
reg_SOCStock <- toolAggregate(iso_SOCStock, rel=iso2reg, from="CountryCode", to="RegionCode")
```

@@

SOCStock <- mbind(glo_SOCStock, reg_SOCStock)
glo_SOC  <- mbind(setNames(SOCStock[,"y2010","actualstate"],"This Study"),
                  setNames(SOCStock[,"y2010","naturalstate"],"This Study (PNV)"),
                  setNames(LPJmL4[,"y2010",], "LPJmL4Paper"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"))

### 2020-12-11 ResultNotebooks/results_SOCmaps.Rmd
update of results images and tables

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)
library(sp)
library(rworldmap)
library(oce) 
library(scales)

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global SOC loss\n in GtC") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-18,0,10),
                     limits = c(-28,0),
                     breaks = c(0, -20, -22, -24, -26, -28)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", size=14, x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

SOCshare <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression(" cropland SOC stock change factor (unitless)"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC gap in tons of carbon per hectare"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("< -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

grid <- plot_grid(SOCdensity, SOCemis, SOCincrease, SOCshare, ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")

>>>>

library(ggplot2)
theme_set(theme_bw())
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(sp)
library(rworldmap)
library(oce) 
library(scales)

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-18,0,10),
                     limits = c(-28,0),
                     breaks = c(0, -20, -22, -24, -26, -28)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

SOCshare <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression("cropland SOC stock change factor (unitless)"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression(paste('croplands \u0394SOC in tons of carbon per hectare')), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("< -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

grid <- plot_grid(SOCdensity,SOCincrease, SOCshare, SOCemis,  ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")

### 2020-12-11 ResultNotebooks/results_SOCscenario.Rmd
update of results images and tables

# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")
# 
for(item in scenarios[10:11]){
   untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
   files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
}

@@

CarbonInput  <- read.magpie(paste0("Data/histManagement/CarbonInput.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[,,"totalC"] * Landuse, dim=c(1)))

@@

readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))

@@

hSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC debt\n in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="bottom", legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0))

@@

vSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1974,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC debt in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

@@

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = "Global SOC debt\n in GtC",
        color    ="Initalitzation",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:2], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

@@

litterSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),litter_scen]), 
                                    aes(x = Year, y = Value, group=Data1, color=Data1, size=Data1)) +
  labs( x = "Year", 
        y = "Global SOC debt\n in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c("red", scen_cols, "blue"), labels = names(litter_scen)) +
  scale_size_manual(values=c(1,rep(0.5, length(litter_scen)-1)), labels = names(litter_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position = "none")

>>>>

# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"), 
#       exdir="Data/histManagement", extras="--keep-newer-files ")
# 
# for(item in scenarios){
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
# }

@@

CarbonInput  <- read.magpie(paste0("Data/histManagement/CarbonInput.rds"))
Landuse      <- read.magpie(paste0("Data/histManagement/Landuse.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[,,"totalC"] * Landuse, dim=c(1)))

@@

@@

hSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="bottom", legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0))

@@

vSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1974,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

@@

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color    ="Initalitzation",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:2], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

@@

litterSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),litter_scen]), 
                                    aes(x = Year, y = Value, group=Data1, color=Data1, size=Data1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c("red", scen_cols, "blue"), labels = names(litter_scen)) +
  scale_size_manual(values=c(1,rep(0.5, length(litter_scen)-1)), labels = names(litter_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position = "none")
